
\chapter{Task B}
A* graph search has being implemented on a recursive manner. 
\section{Environment changes}
The main environment will not change from task A. This agent still works on Vertices and Edges. The difference is the way of storing the path. 
The agent in task A stores it in an open list, in the other hand the agent in this case stores the final path in a closed list. The lists 
implemented in this case are bidirectional so the traversal can be done both ways.

\section{Agent description}

The agent contains, as shown on the picture, the following fields:\\
\begin{description}
\item[Fringe:]Open list used in the heuristic, for which we use the shortest path algorithm. The fringe is a pointer to a list of Node, 
a struct described in agent.h and on the picture.
\item[Open:]Open list used in the A* algorithm. It's also a list of Nodes like the fringe.
\item[Closed:]Closed list used to store the final path to the goal. As the Open list and the fringe the closed list is a list of struct Node.
\item[Goal:]Pointer to the goal vertice, is used for compairesons during the hole A* algorithm.
\item[Environment:]Pointer to the beginning of the vertice list. It contains the  environment and is used constantly.
\end{description}

To make the agent be able to execute the A* algorithm we created some helper functions:\\

\begin{description}
\item[findShortest:]Function used to calculate the heuristic value for the A* graph search. Recursivly it stacks values in the Fringe 
and pops from there, until it finds the goal. It gives the total cost of the shortest path in return. It executes recursivly be making a call 
to itself poping the next element in the fringe.
\item[pop:]Funtion that returns the last element in the fringe or the open list, depending on the value of the parameter mode. After 
taking the Node out of the list the list pointer is moved frontwords to the next most probable value.
\item[push:]Function that puts new elements in the lists, it aranges it acording to the cost field int the Node struct. Depending on the 
value provided in the mode parameter the function stores the new element in the fringe or in the open list.
\item[recursive:]Recursive function for calculating the A* graph search algorithm.
\end{description}


\section{A* Star Graph Search algorithm}


